Project Proposal

### 2024-11-17 NFL_IDS702Projectproposal.qmd
box plots

# Create the individual plots
plot1 <- ggplot(nfldata, aes(x = factor(down), y = homeTeamWinProbabilityAdded)) +
  geom_boxplot(fill = 'purple') +
  labs(x = "Down", y = "Home Team Win Probability Added") + 
  theme(plot.margin = margin(t = 20, r = 30, b = 20, l = 10),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8))

plot2 <- ggplot(nfldata, aes(x = factor(quarter), y = homeTeamWinProbabilityAdded)) +
  geom_boxplot(fill = "green") +
  labs(x = "Quarter", y = "Win Probability") +
  theme(plot.margin = margin(t = 20, r = 20, b = 20, l = 20),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8))

>>>>

# Create the individual plots
plot1 <- ggplot(nfldata, aes(x = factor(down), y = homeTeamWinProbabilityAdded)) +
  geom_boxplot() +
  labs(x = "Down", y = "Home Team Win Probability Added") + 
  theme(plot.margin = margin(t = 20, r = 30, b = 20, l = 10),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8))

plot2 <- ggplot(nfldata, aes(x = factor(quarter), y = homeTeamWinProbabilityAdded)) +
  geom_boxplot() +
  labs(x = "Quarter", y = "Win Probability") +
  theme(plot.margin = margin(t = 20, r = 20, b = 20, l = 20),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8))
